### 2022-11-13 NSF2022/Description/backgroundv3.tex
SA1, SA2, and bibliography

To determine how the granules move through space,
we look for rigid body transformations
\begin{align}
\label{eq:RBT}
  F_i(\XX,t) = R_i(t)(\XX - \aa_i(0)) + \aa_i(t),\quad \XX \in U_i(0),
\end{align}
where $i = 1,\ldots,N_b,$ $R_i(t)$ is an $n
\times n$ rotation matrix, $\aa_i(t)$ are the granule centers, and $\XX$ is a
reference coordinate.
The dynamics come from the following system of semi-linear, elliptic boundary value problems:
\begin{alignat}{4}
  \label{eqn:stokes} 
  -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
  \quad \nabla \cdot \uu = 0, &&\xx \in \Omega(t), \\
  \label{eqn:phase}
  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, &&\xx \in \Omega(t),\\
  \label{eqn:noslip}        
  \frac{dF_i}{dt}(\XX,t) & = \uu(\xx) = 
    \vv_i + \omega_i \times (\xx - \aa_i), 
  \quad &&\xx \in \Gamma_i(t),\\
  \label{eqn:material}
  \phi(\xx) &= h_i(\XX),  &&\xx \in \Gamma_i(t),
\end{alignat}
for $i=1,\ldots,N_b$ and where $\xx = F_i(\XX,t)$.  Finally,
\begin{align}
\label{eqn:stressbalance}
\int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif s = \mathbf{0},\quad
\int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu \,\dif s = \mathbf{0}
\end{align}
where
\begin{align}
\label{eqn:hydro_stress}
\sigma = \mu(\nabla \uu + \nabla \uu^T) - pI,\quad 
T_i = \gamma\left[\epsilon^{-1} W'(\phi)I
  + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
  \phi^T\right)\right]
\end{align}
are the hydrodynamic and phase field stresses, respectively.
Equations~\eqref{eqn:stokes} are the Stokes equations 
describing the velocity $\uu$ and pressure $p$ of
the incompressible fluid region with viscosity $\mu$.
Equation~\eqref{eqn:phase} describes the
transitions of the scalar order parameter $\phi$ with a decay length
$\epsilon$.
The scalar function $W(\phi) : \mathbb{R} \to \mathbb{R}$ is a nonnegative
well-potential with local minima $\phi_0, \phi_1$  etc.
representing metastable states of the solvent.
For the single well case, $W(\phi) = \frac{1}{2}\phi^2$
has the minimum $\phi_0 = 0$ and the phase field equation
\eqref{eqn:phase} becomes the \emph{linear} screened Laplace equation.
For the double well case e.g, $W(\phi) = \frac{1}{4}(\phi^2-1)^2+cx$, $c > 0$,
the phase field equation \eqref{eqn:phase} takes the form of an
Allen-Cahn equation with local minima $\phi_0 < 0 < \phi_1$.
Section \ref{sec:specific_aim1} discusses certain
modifications needed for \eqref{eqn:phase} in the nonlinear case.

@@

\begin{wrapfigure}[22]{r}{3.2in}
  \vspace{-15pt}
  \begin{center}
    \begin{tabular}{m{0.9in}m{0.9in}m{0.9in}}                 
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B3.jpg}    \\
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C3.jpg}    \\
      \includegraphics[width=0.85in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A3.jpg} 
  \end{tabular}
  \end{center}
  \vspace{-15pt}
  \caption{\footnotesize \label{fig:self-assembly2}
  Changes in the boundary condition \eqref{eqn:material}
  yield distinct morphologies.
  Each row has the same initial configuration, $W(\phi) = \tfrac{1}{2}\phi^2$.
  (\emph{Top}) Granules with an amphiphilic boundary condition
  results in a bilayer pattern (yellow,
  $\phi = 1$, blue, $\phi = 0$).
  (\emph{Middle}) Granules with $\phi = 2$ (magenta) on one side and $\phi = 1$
  on the other   form multilamellar bilayers.
  (\emph{Bottom}) Bipolar granules with $\phi = \pm 1$ (yellow, green, resp.)
  on poler ends   form a checkerboard pattern.}
\end{wrapfigure}
\subsection{Applications}
Since the framework is scale independent, it can be applied broad
range of nonspecific self-organization phenomena in surface chemistry,
biology and engineering. For one, the
formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
the right behavior expected from amphiphilic self-assembly.
For example, three bodies with amphiphilic label (\S\ref{sec:specific_aim1})
spontaneously self-organize to sequester the hydrophobic fluid phase
(Figure~\ref{fig:flow_map}).
Changes in the boundary conditions result in
distint morphologies
(Figure~\ref{fig:self-assembly2})
whose rheology can be further investigate (\S\ref{subsec:specific_aim_3}).

>>>>

To determine how the granules move through space,
we look for rigid body transformations
\begin{align}
\label{eq:RBT}
  F_i(\XX,t) = R_i(t)(\XX - \aa_i(0)) + \aa_i(t),\quad \XX \in U_i(0),
\end{align}
where $i = 1,\ldots,N_b,$ $R_i(t)$ is an $n
\times n$ rotation matrix, $\aa_i(t)$ are the granule centers, and $\XX$ is a
reference coordinate.
The dynamics come from the following system of semi-linear, elliptic boundary value problems:
\begin{alignat}{4}
  \label{eqn:stokes} 
  -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
  \quad \nabla \cdot \uu = 0, &&\xx \in \Omega(t), \\
  \label{eqn:phase}
  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, &&\xx \in \Omega(t),\\
  \label{eqn:noslip}        
  \frac{dF_i}{dt}(\XX,t) & = \uu(\xx) = 
    \vv_i + \omega_i \times (\xx - \aa_i), 
  \quad &&\xx \in \Gamma_i(t),\\
  \label{eqn:material}
  \phi(\xx) &= h_i(\XX),  &&\xx \in \Gamma_i(t),
\end{alignat}
for $i=1,\ldots,N_b$ and where $\xx = F_i(\XX,t)$.  Finally,
\begin{align}
\label{eqn:stressbalance}
\int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif s = \mathbf{0},\quad
\int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu \,\dif s = \mathbf{0}
\end{align}
where
\begin{align}
\label{eqn:hydro_stress}
\sigma = \mu(\nabla \uu + \nabla \uu^T) - pI,\quad 
T_i = \gamma\left[\epsilon^{-1} W'(\phi)I
  + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
  \phi^T\right)\right]
\end{align}
are the hydrodynamic and phase field stresses, respectively.
Equations~\eqref{eqn:stokes} are the Stokes equations 
describing the velocity $\uu$ and pressure $p$ of
the incompressible fluid region with viscosity $\mu$.
Equation~\eqref{eqn:phase} describes the
transitions of the scalar order parameter $\phi$ with a decay length
$\epsilon$.
The scalar function $W(\phi) : \mathbb{R} \to \mathbb{R}$ is a nonnegative
well-potential with local minima $\phi_0, \phi_1$  etc.
representing metastable states of the solvent.
For the single well case, $W(\phi) = \frac{1}{2}\phi^2$
has the minimum $\phi_0 = 0$ and the phase field equation
\eqref{eqn:phase} becomes the \emph{linear} screened Laplace equation.
For the double well case e.g, $W(\phi) = \frac{1}{4}(\phi^2-1)^2+cx$, $c > 0$,
the phase field equation \eqref{eqn:phase} takes the form of an
Allen-Cahn equation with local minima $\phi_0 < 0 < \phi_1$.
Section \ref{sec:specificaim1} discusses certain
modifications needed for \eqref{eqn:phase} in the nonlinear case.

@@

\begin{wrapfigure}[22]{r}{3.2in}
  \vspace{-15pt}
  \begin{center}
    \begin{tabular}{m{0.9in}m{0.9in}m{0.9in}}                 
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100B1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B2.jpg}
     &\includegraphics[width=0.85in]{figures/SpecificAim1/N100B3.jpg}    \\
    \includegraphics[width=0.85in]{figures/SpecificAim1/N100C1.jpg}
    &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100C3.jpg}    \\
      \includegraphics[width=0.85in]{figures/SpecificAim1/N100A1.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A2.jpg}
      &\includegraphics[width=0.85in]{figures/SpecificAim1/N100A3.jpg} 
  \end{tabular}
  \end{center}
  \vspace{-15pt}
  \caption{\footnotesize \label{fig:self-assembly2}
  Changes in the boundary condition \eqref{eqn:material}
  yield distinct morphologies.
  Each row has the same initial configuration, $W(\phi) = \tfrac{1}{2}\phi^2$.
  (\emph{Top}) Granules with an amphiphilic boundary condition
  results in a bilayer pattern (yellow,
  $\phi = 1$, blue, $\phi = 0$).
  (\emph{Middle}) Granules with $\phi = 2$ (magenta) on one side and $\phi = 1$
  on the other   form multilamellar bilayers.
  (\emph{Bottom}) Bipolar granules with $\phi = \pm 1$ (yellow, green, resp.)
  on poler ends   form a checkerboard pattern.}
\end{wrapfigure}
\subsection{Applications}
Since the framework is scale independent, it can be applied broad
range of nonspecific self-organization phenomena in surface chemistry,
biology and engineering. For one, the
formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
the right behavior expected from amphiphilic self-assembly.
For example, three bodies with amphiphilic label (\S\ref{sec:specificaim1})
spontaneously self-organize to sequester the hydrophobic fluid phase
(Figure~\ref{fig:flow_map}).
Changes in the boundary conditions result in
distint morphologies
(Figure~\ref{fig:self-assembly2})
whose rheology can be further investigate (\S\ref{sec:specificaim3}).

### 2022-11-13 NSF2022/Description/specificaim2.tex
SA1, SA2, and bibliography

To briefly describe IE formulations of PDEs, we consider the Stokes
equation~\eqref{eqn:stokes} as an example. Its solution can be written
as a convolution 
\begin{align*}
  \uu(\xx) = \int_{\partial\Omega(t)} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
\end{align*}
where $G(\xx - \yy)$ is a carefully chosen derivative of the PDE's
fundamental solution and $\ssigma: \partial \Omega(t) \rightarrow \RR^2$
is an unknown density function. The IE reformulation has several
immediate advantages including a dimension reduction since $\ssigma$ is
defined only on $\partial \Omega(t)$, and the far field boundary
condition of the PDE is automatically satisfied. The density
function $\ssigma$ is chosen to satisfy the boundary condition, and this
results in an IE 
\begin{align*}
  \gg(\xx) = \lambda \ssigma(\xx) + 
    \int_{\partial\Omega(t)} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
    \quad \xx \in \partial\Omega(t),
\end{align*}
where $\gg$ is the boundary condition, and $\lambda$ is a constant that
depends on the choice of $G$. For numerical stability, choices of $G$
that result in second-kind Fredholm integral equations, meaning $\lambda
\neq 0$, are preferred.

>>>>

To briefly describe IE formulations of PDEs, we consider the Stokes
equation~\eqref{eqn:stokes} as an example. Its solution can be written
as a convolution 
\begin{align*}
  \uu(\xx) = \int_{\partial\Omega(t)} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
\end{align*}
where $G(\xx - \yy)$ is a carefully chosen derivative of the PDE's
fundamental solution and $\ssigma: \partial \Omega(t) \rightarrow \RR^2$
is an unknown density function. This is analogous to the problem of
finding the global electrostatic potential $u$ with surface charge
density $\sigma$
\begin{align*}
  u(x) = -\frac{1}{4\pi}\int_{\partial \Omega(t)} 
    \frac{1}{|\xx - \yy|}\sigma(y) \, ds_\yy.
\end{align*}

The IE reformulation has several immediate advantages including a
dimension reduction since $\ssigma$ is defined only on $\partial
\Omega(t)$, and the far field boundary condition of the PDE is
automatically satisfied. The density function $\ssigma$ is chosen to
satisfy the boundary condition, and this results in an IE 
\begin{align}
  \gg(\xx) = \lambda \ssigma(\xx) + 
    \int_{\partial\Omega(t)} G(\xx - \yy) \ssigma(\yy) \, ds_\yy,
    \quad \xx \in \partial\Omega(t),
  \label{eqn:bie}
\end{align} where $\gg$ is the boundary condition, and $\lambda$ is a
constant that depends on the choice of $G$. For numerical stability,
choices of $G$ that result in second-kind Fredholm integral equations,
meaning $\lambda \neq 0$, are preferred. Returning to electrostatics,
equation~\eqref{eqn:bie} is analogous to Gauss's Law that relates the
electrostatic potential on $\bd \Omega(t)$ to the surface charge
density.
